Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-03 manuscript.Rmd
some updates

>>>>

test building of gene sets

```{r}
targetedGeneSets <- AMPAD::collateEnrichmentSets()
```

Plot from Figure 1c
```{r}
synapser::synLogin()
modMeta <- AMPAD::getModuleMetainfo('syn11932957')
dummyDf <- targetedEnrichment$cell
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf$category <- gsub('Zhang\\.','',dummyDf$category)
dummyDf$category <- factor(dummyDf$category,levels = rev(c('Astrocyte',
                                                       'Endothelial',
                                                       'Microglia',
                                                       'Neuron',
                                                       'MyelinOligos',
                                                       'NewOligos',
                                                       'OPC')))
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Cell Type Signature')
g
```
